### 2025-08-22 sec/related-work.tex
Beramono.
Start on related work categories.

\todo{flesh out}

\begin{itemize}
\item Transparent visualisations \cite{perera22,bond24}
\end{itemize}

>>>>

\paragraph{Interpretable NLP.}

Recent advances in interpretable language understanding, highlighting the shift from fine-tuning to
prompt-based learning in NLP and presenting research on improving the transparency of neural models through
interpretable classifiers, uncertainty analysis, and explainable systems. \cite{Yulan_2023}

\paragraph{AI interpretation of scientific text.}

For example quantity extraction~\cite{bolucu-etal-2023-investigating}, scientific fact-checking
\cite{abu-ahmad-etal-2025-climatecheck-shared}.

\paragraph{Linguistic competences of LLMs.}

\paragraph{Transparent programming languages.}

\cite{perera22,bond25,psallidas18smoke}
